\documentclass[12pt]{article}
\pagestyle{empty}

\begin{document}

\section*{Comment regarding the abstract}

I just finished reseraching and writing a broad talk on early
discoveries at CMS, where I took as a driving criterion ``what can be
done with 100~pb$^{-1}$?''

After submitting the talk, I saw the pre-prepared abstract for the
first time:

\begin{quote}
This presentation will summarize the latest studies of CMS for early
discoveries of New Physics. The survey will cover new gauge boson
production (Z', W'), searches for signals in extra dimensions from RS
and ADD models, heavy neutrinos, bprime production and new
signatures. The studies are performed assuming an accumulated
luminosity of a few 100 pb-1 or less.
\end{quote}

I don't know how I didn't see this abstract before; I've been looking
for it for weeks now, and finally assumed that wasn't one.  (It's
displayed automatically after uploading a talk.)

Is the outline of this talk acceptable as it is?  I can append slides
for $W' \to e\nu$ and $b' \to WWWW$ and stay within 20~minutes without
much trouble (though these are busy slides: more than 1 minute each).

I remember seeing work on heavy neutrinos in the slides and twiki
pages I read while researching the talk, but I don't see anything
about it on the PhysicsResults twiki page, and I don't remember seeing
any results for as little as 100~pb$^{-1}$.  Is there a note/PAS I
should read?  Thanks!

\vspace{0.5 cm}
--- Jim Pivarski $<$pivarski@physics.tamu.edu$>$

\vspace{0.5 cm}
(I'm sending this through the CINCO page to have the same readership
as the talk.)

\end{document}
